\documentclass[]{article}
\usepackage{graphicx}

\parindent=0pt
\usepackage[margin=0.5in]{geometry}
\usepackage{url}
\usepackage{hyperref}

\begin{document}
\pagestyle{empty}
{\large\textbf{Research Notes}}
\begin{itemize}
    \item[*] Created on Mon 04 Jan 2016 11:23:25 AM EST
    \item[*] Modified on \today
    \item[*] Author info: Boyou Zhou\\
             8 St Mary's St, PHO 340, Boston, MA 02215\\
             Email: bobzhou@bu.edu, Phone: 617-678-8480\\
\end{itemize}

\rule[-0.1cm]{7.5in}{0.01cm}\\
\noindent \textbf{Mon 04 Jan 2016 11:14:43 AM EST}
\textit{Beginner's tutorial of AXI slave logic design}

This documents gives a brief instruction of how to design an AXI slave logic on
Zedboard. Zedboard provides two ARM cores and programmable logic. From here, ps
stands for GPP, ARM in this case, pl for programmable logic.\ 

Ps and Pl are connected with AXI ports. In this design, our logic talks to the
ps with AXI ports.\ ps looks at the logic as memory blocks. More strictly, the ps
visit the logic registers as memory units. On the ps side, I used a full linux,
Linaro Linux as the os for ps. The programs are run on the ps interfacing the
memory units through AXI ports, $/dev/mem$

Here are the tutorials to the design.
\indent		\begin{itemize}
			\item \textit{Start Linux}
			\url{http://fpga.org/2013/05/24/yet-another-guide-to-running-linaro-ubuntu-desktop-on-xilinx-zynq-on-the-zedboard/}
			\item \textit{AXI Slave Logic}
			\url{http://www.fpgadeveloper.com/2014/08/creating-a-custom-ip-block-in-vivado.html}
			\item \textit{Visit Memory Block}
			\url{http://fpga.org/2013/05/28/how-to-design-and-access-a-memory-mapped-device-part-one/}
        \end{itemize}

The device tree design, we do not include adv7511.dtsi in zynq-zed-adv7511.dtsi

\noindent \textbf{Thu 07 Jan 2016 12:38:46 PM EST}
\textit{Papers related to security}
\begin{itemize}
	\item side channel detection \cite{longo2015soc} 
	\item encoding methods \cite{chakraborti2015trivia} 
	\item radio security breach \cite{genkin2015stealing}
	\item PUF \cite{aysu2015end} \cite{maes2015secure} \cite{herder2014physical} \cite{devadas2010secure}
	\item SAT \cite{saha2015improved}
	\item TRNG \cite{haddad2015physical}\cite{suh2007physical}\cite{herder2014trapdoor}
	\item new tech \cite{suh2003efficient}
	
\rule[-0.1cm]{7.5in}{0.01cm}\\
\\
	\item coprocessor \cite{roy2015lightweight} 
	\item break RSA on Intel chip \cite{bhattacharya2015watches}
	\item accelerating homomorphic encryption \cite{doroz2015accelerating}
	\item memory verification and encryption, verification ensures the
adversary changes in the machine states. Encryption protects the off-chip
memory\cite{suh2003efficient}

\end{itemize}

some explanation
\begin{itemize}
	\item \cite{herder2014trapdoor}TRNG: safely extract the keys from biometric source
\end{itemize}

\rule[-0.1cm]{7.5in}{0.01cm}\\
\noindent \textbf{Mon 01 Feb 2016 09:55:39 AM EST}
\textit{Architecture people working on security}

\begin{itemize}
	\item Srini Devdas (MIT) \url{https://scholar.google.com/citations?user=-yrzguMAAAAJ&hl=en}
	\item Edward Suh (Cornell) \url{https://scholar.google.com/citations?user=neO3vFYAAAAJ&hl=en&oi=ao}~\cite{chen2015execution}
	\item Mohit Tiwari (U T Austin)
	\item Simha Sethumadhavan (Columbia)
	\item Tim Sherwood (UCSB)
	\item Dawn Song (U C Berkeley)
\end{itemize}

In the homomorphic computation, somewhat homomorphic function evaluation needs to be reviewed.\textbf{SHF}
\begin{itemize}
	\item \cite{chen2015execution} gives the 
\end{itemize}

\rule[-0.1cm]{7.5in}{0.01cm}\\
\noindent \textbf{Mon 22 Feb 2016 01:59:29 PM EST}
\textit{papers on architecture security}
\begin{itemize}
	\item \cite{wang2014timing} RSA attacks: each RSA decoding will result in
memory access. Thus the number of access in memory is the hamming distance of
RSA keys.
	\item \cite{ismail2015improving} 
	\item \cite{ancajas2014fort} thread model: HTs attachs one of the cores and
propagate information to other cores.  Defence model: Data scrambling as the
first layer, dynamic packet certificate as the second layer, and node
obfuscation on the third layer
\end{itemize}

\bibliography{week1}{}
\bibliographystyle{plain}
\end{document}

